### 2010-09-17 proposal/preProposal.tex
edits with S and D

To this end, we will use machine learning to design a gait for a
quadraped robot, available from Hod Lipson's lab.  We anticipate using
speed and efficiency as metrics for evaluation of the designed gait;
these metrics are presented further in Section~\ref{sec:evaluation}.

@@

\section{General approach}

@@

We will be working with a robot that has an on-board computer running Linux. The lower level drivers are in C and we hope to implement the system in Python.

Once we begin working with the robot and have an idea of the algorithm we will use, we will divide the work.

>>>>

To this end, we will use machine learning to design a gait for a
quadraped robot, available from Hod Lipson's lab.  We anticipate using
speed and efficiency as metrics for evaluation of the designed gait;
these metrics are presented further in Section~\ref{sec:evaluation}.
The robot learning will be accomplished via one of several machine
learning algorithms, discussed in Section~\ref{sec:approach}.

@@

\section{General approach}
\label{sec:approach}

@@

We will be working with a robot that has an on-board computer running
either Windows or Linux. The lower level drivers are in C and we hope
to implement the system in Python.

Once we begin working with the robot and have an idea of the algorithm
we will use, we will divide the work among us.
